Are We Reusing Outdated and Licensed Code from Stack Overflow?

### 2017-02-23 cloneoverflow-latex/cloneoverflow.tex
Lots of restructuring according to Rocco's comments. Sent to Jens before Chaiyong going to the SANER banquet.

%\subsection{Experimental Setup}
%\vspace{1ex}
To answer these four research questions, we perform an empirical study to
locate and study the online code clones between Stack Overflow and open source
projects. The experimental framework is depicted in \Cref{fig:exp_framework} and
we discuss our experimental setup below.

@@

\subsection{Datasets}

@@

\subsubsection{Stack Overflow}

We extracted Java code snippets from a snapshot of a Stack Overflow
dump\footnote{\url{https://archive.org/details/stackexchange}} in
January 2016. The archived dump has a size of 9 gigabytes. The data
dump is in XML format containing information of \textbf{Posts}
(questions and answers) and supporting data such as user accounts and
timestamps of the posts. We were interested in code snippets embedded
in posts which were located between
{\small\texttt{<code>}...\texttt{</code>}} tags. A Stack Overflow
thread contains a question and several answers. An answer can also be
marked as \textbf{accepted answer} by the questioner if the solution
fixes his/her problem. We collected Java code snippets using two
criteria. First, we only focused on code snippets in accepted
answers. We chose the snippets in accepted answers because they
actually solved the problems in the questions. Moreover, they are
always displayed just below the questions which makes them more
likely to be reused than other answers. Second, we were only
interested in code snippets of at least six lines. Snippets smaller
than six lines are usually spurious clones~\cite{Bellon2007}. Each
snippet was extracted from the dump and saved to a file.
%using its post ID as the file's name. If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g. 45051109\_0, and 45051109\_1.). Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them. 
We obtained 144,064 Java code snippets containing 2,347,267
lines\footnote{Measured by cloc:
  \url{https://github.com/AlDanial/cloc}} of Java source code.
% excluding comments and blank lines.

\subsubsection{Open source systems}

We selected the established corpus for an empirical software
engineering study called \textbf{Qualitas}~\cite{QualitasCorpus} for
this study. It is a curated Java corpus that has been used in several
software engineering
studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. The
projects in the corpus represent various domains of software systems
ranging from programming languages to
visualisation~\cite{QualitasCorpus}. We selected the 20130901r release
of Qualitas corpus containing 112 Java open source projects. This
release contains projects with releases no later than 1st September
2013. We chose a snapshot late back in 2013 since we are interested in
online code clones in the direction from open source projects to Stack
Overflow. The 20130901r snapshot provides Java code that is more than
2 years older than the Stack Overflow snapshot, which is sufficiently
long for a number of code snippets to be copied onto Stack Overflow
and also to observe if clones become outdated. Out of 112 Qualitas
projects, there is one project, \textsf{jre}, that does not contain
Java source code due to its licensing limitation~\cite{QualitasCorpus}
and is removed from the study. This resulted in a total of 111
projects analysed in the study. As shown in \Cref{tab:datasets}, the
111 Qualitas project have 160,937 Java files containing 19,086,883
lines of
code. %Details of the 109 Qualitas projects and their licenses are listed in Table \ref{t:new_and_old}.

@@

To answer the four research questions, we derived three result sets; 
\textit{Reported Clones}, \textit{Filtered Clones}, and \textit{Pattern Clones};
and a manual investigation of online clones. 
For the Reported Clones set, we deployed code clone detection
to locate similar code,~i.e.~clones, between Stack Overflow and 
Qualitas projects. The second result set, Filtered Clones, is derived from the
Reported Clones set by filtering out trivial clones. The last result set,
Pattern Clones, is used to define the online code cloning patterns
for our manual classification. We show the number of clone pairs in the Reported Clones,
Filtered Clones and Pattern Clone result set in \Cref{tab:result_sets}.

With the Reported Clones and Filtered Clones result sets, 
we can observe how many code snippets on
Stack Overflow are reported as clones to/from Qualitas projects
in two aspects: before and after removing trivial clones. 
We explain the approach we used to create to two result sets below.

\begin{table}
	\centering
	\caption{Clone Result Sets}
	\label{tab:result_sets}
	%\small
	\begin{tabular}{lp{3cm}r}
		\hline 
		Result set & Description & Clone pairs \\
		\hline
		Reported Clones & All reported clones & 315,786,118 \\ 
		%\hline 
		Filtered Clones & Clones after filtering & 32,533 \\ 
		Pattern Clones & Clones for defining online cloning patterns & 697 \\
		\hline 
	\end{tabular} 
\end{table}

\subsubsection{Reported Clones Result Set} 
We use clone detection to discover online code clones. 
%\textbf{Clone Detection and Configuration: } 
There are a number of restrictions in terms of choosing clone
detection tools for this study. The main restriction is due to nature
of code snippets posted on Stack Overflow, as most of them are
incomplete Java classes or methods. Hence, a detector must be flexible
enough to process code snippets that are not compilable or not
complete blocks. Moreover, since the amount of code that has to be
processed is in a scale of millions line of code (as shown in
\Cref{tab:datasets}), a clone detector must be scalable enough to
report clones in a reasonable amount of time. We have tried 5
state-of-the-art clone detectors including Simian~\cite{simian},
NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002},
iClones~\cite{Gode2009}, and DECKARD~\cite{Jiang2007a} against the
Stack Overflow and Qualitas datasets. CCFinder, iClones, and DECKARD
failed with execution errors after running for couple of hours. Thus,
we removed them from the study. Simian and NiCad are flexible enough
to handle code with incomplete methods or classes and successfully
completed the detection.

@@

%We processed two datasets, 144,064 Java code snippets from accepted answers on Stack
%Overflow and 111 open source projects from the Qualitas corpus. 
%The Java code snippets were extracted from Stack Overflow posts. 
We prepared the Java code in both datasets by removing comments and
pretty-printing to increase the accuracy of clone detection. Then, we
deployed the two clone detectors to locate clones between the two
datasets. Due to a scalability issue, we partitioned the input and ran the tools multiple
times. Each run was composed of the entire Stack Overflow data and a
single Qualitas project. We repeated the process until we covered all
111 projects.  We then converted the clone reports to the General
Clone Format (GCF)~\cite{Wang2013} and combined the 111 reports into a
single GCF file.  Simian did not provide an option to detect
cross-project clones between two locations. Hence the Simian GCF clone
report was filtered to contain only clone pairs between Stack Overflow
and Qualitas projects, removing all clone pairs within either Stack
Overflow or within Qualitas. 
% NiCad provides an option to detect clones
% from two locations so no filtering was needed.
%\subsection{Clone Detection Configuration}

We were aware of effects of configurations to clone detection results
and the importance of searching for optimised configurations in
empirical clone
studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016}. However,
considering the massive size of the two datasets and the search space
of at least 15 Simian and 5 NiCad parameters, we are unable to search
for the best configurations of the tools. Thus, we decided to
configure Simian and NiCad using two established configurations:
(1)~the tools' default configurations chosen by the tools' creators
(denoted as \textit{D}), and (2)~the discovered configurations for
Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
of optimising clone detectors' configurations based on clone agreement
(denoted by \textit{E}). The details of the two configurations are
described in \Cref{t:param_tuning}.

@@

\subsubsection{Filtered Clones Result Set}

As there are in total 315,786,118 clone pairs reported, it is
infeasible for humans to manually validate them all. Instead of
investigating a random saple, we adopted the idea of \textbf{clone
  agreement} which has been used in clone research
studies~\cite{Funaro2010, Wang2013,cr2016ssbse} in situations where a
clone oracle is missing or impossible to establish. Clone pairs agreed
by multiple clone detection tools have a higher likelihood to be real
clones~\cite{cr2016ssbse}. By using this agreement-based approach, we
reduced the number of clone candidates for manual investigation to the
ones agreed by multiple tools. To find agreement between two clone
pairs reported by two different tools, we used the clone pair matching
metric proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs
which have a large enough number of overlapping lines can be
categorised as either a good-match or an ok-match pair (denoted as
\textit{good} and \textit{ok} respectively) with a confidence value
between 0 and 1. A \textit{good} clone pair has stronger agreement
than an \textit{ok} pair. We follow the original definitions of good-
and ok-match introduced in Bellon's paper~\cite{Bellon2007}.

@@

%\subsubsection{Filtered Clones Set}
We selected all \textit{good} pairs (2,313) and the \textit{ok} pairs for
$S_D$--$N_D$, $S_E$--$N_D$, and $S_D$--$N_E$ (12,336), but we ignored
20,021 $S_EN_E$ \textit{ok} clone pairs in the classification due to
their large number of clones and the very small average clone sizes of
5.95 and 6.28 lines (see \Cref{tab:orig_stats}), leading to a high
probability of being trivial clones. We refer to the set of clone
pairs as the \textit{good} set and the \textit{ok'} set.
Together with the 17,801 (referred as $S_D'$ set) and 83 (referred as
$N_D'$ set) clone pairs after filtering clone pairs from $S_D$ and
$N_D$, we ended up with a set of 32,533 online clone pair candidates
for manual inspection.

@@

\subsection{RQ2: Patterns of Online Code Cloning}
As we are interested in the patterns of online code clones, we studied
the 8 patterns of cloning from Kapser et
al.~\cite{Kapser2006,Kapser2008} and performed a preliminary study to
evaluate its applicability to our study by using a small subset of the
reported online clones.

\subsubsection{Pattern Clones Result Set}
Using the $S_D$ clone report,
snippets were ranked according to (1)~clone pair frequency,
(2)~popularity (i.e.~number of associated Qualitas projects),
(3)~clone size in SLOC, and (4)~ratio of cloned code per snippet. We
selected these four criteria so that we could cover the online clones
from various aspects. We selected the top 10 from each ranking and
obtained 34 unique Stack Overflow snippets. The snippets were
associated with 697 clone pairs.

\subsubsection{Defining Online Code Cloning Patterns}
Using Kapser's cloning patterns and the Pattern Clones Result Set, the
clone pairs were categorised into either Customisation or Templating.
However, Kapser's cloning patterns are too broad for our study and a
more suitable and fine-grained classification scheme is needed. After
the preliminary study, we adopted one of Kapser's cloning patterns,
\emph{boiler-plate code} and \emph{API/library protocol}, and defined
6 new cloning patterns. The seven patterns include QS, SQ, EX, UD, BP,
IN, and AC as presented in \Cref{tab:classification_scheme}. Pattern
QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones
that have evidence of being copied from a Qualitas project to Stack
Overflow. The evidence of copying can be found in comments in the
Qualitas source code or in the Stack Overflow post's contents. Pattern
SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is cloning, with
evidence, in the opposite direction from Stack Overflow to a Qualitas
project. Pattern EX (\textbf{Ex}ternal Sources) is cloning that has
evidence of copying from a single or multiple external sources to
Stack Overflow and to a Qualitas project.  Pattern UD
(\textbf{U}nknown \textbf{D}irection) is cloning that creates
identical or highly similar clones between Qualitas and Stack Overflow
but where we could not find any attribution of copying.

Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones
containing boiler-plate code of {\small\verb|equals()|} methods,
getters/setters, or IDE-generated code such as GUI components. Pattern
IN (\textbf{In}heritance/Interface) is cloning by inheritance of the
same super class or implementation of the same interface. These two
activities usually result in similar overriding methods. The last
pattern, AC (\textbf{A}ccidental \textbf{C}lones), represents
accidentally similar clone pairs. These are mainly false positive
clones from the clone detectors such as similar
{\small\texttt{try-catch}} statements.

The first author, who has been working on clone detection research for 
two years, took the role of the main investigator performing a manual 
classification of the filtered clone pairs. By consulting the cloning 
patterns, the main investigator went through each clone pair candidate, 
looked at the clones, and chose the most appropriate cloning pattern 
for the pair. To mitigate the human errors of the manual classification, 
the second author took the role of the validating investigator, performing a
validation on 10\% of the clone pairs judged by the main
investigator. After the validation, the classifications from the two
investigators were compared and conflicts were discussed and resolved.
If the two investigator cannot find a consensus, the third author is 
involved for the final judgement.

@@

We used the experimental framework (\Cref{fig:exp_framework}) to
detect clones between Stack Overflow and the Qualitas corpus using the
two selected clone detectors. To answer RQ1, we computed statistics on
discovered clones. To answer RQ2, we manually investigated online
clone pair candidates and categorised them using patterns of online
code cloning. For RQ3, we looked at the true positive clone pairs and
checked if they have been changed since they have been
cloned. Similarly, for RQ4, we looked at the license of each clone and
checked for a possibility of a licensing violation.

@@

\begin{table}
\caption{Investigated online clone pairs and corresponding snippets
  and Qualitas projects for the different data sets}
\label{tab:snippets}
\centering
\begin{tabular}{l|rrrr}
  \hline 
  Data Set & Pairs & Snippets & Projects & Avg.~C$_{\textrm{\textit{\%}}}$ \\
  \hline 
  \multicolumn{5}{l}{\textit{Reported Clones}} \\
  \hline
  $S_D$ & 67,570 & 1,086 & 92 & 38\% \\
  $S_E$ & 63,635,844 & 1,531 & 111 & 50\% \\
  $N_D$ & 632,855& 1,392 & 88 & 30\% \\
  $N_E$ & 251,449,849& 12,886 & 88 & 33\% \\
  \hline
  Total & 315,786,118 & 14,856 & 111 & 38\% \\
  \hline
  \multicolumn{5}{l}{\textit{Filtered Data Sets}} \\
  \hline
  \textit{good} & 2,313 & 97 & 67 & 23\% \\
  \textit{ok'} & 12,336 & 139 & 43 & 28\% \\
  $S_D'$ & 17,081 & 460 & 74 & 31\% \\
  $N_D'$ & 83 & 44 & 19 & 27\% \\
  \hline
  Total & 32,533 & 623 & 96 & 27\%\\
  \hline 
  \multicolumn{5}{l}{\textit{True Positives without AC}} \\
  \hline 
  $\textit{good}/\textrm{AC}$ & 141 & 52 & 26 & 23\% \\
  $\textit{ok'}/\textrm{AC}$ & 12,229 & 126 & 36 & 28\% \\
  $S_D'/\textrm{AC}$ & 17,673 & 448 & 72 & 31\% \\
  $N_D'/\textrm{AC}$ & 70 & 39 & 16 & 29\% \\
  \hline
  Total & 30,113 & 556 & 80 & 28\% \\
  \hline
\end{tabular}
\end{table}

However, using Bellon's criteria for matching clone pairs, only
0.1\textperthousand~of all pairs are agreed by two tool/configuration
combinations. As shown in \Cref{tab:snippets}, for the 2,313
\textit{good} pairs, there are 97 Stack Overflow snippets which are
associated with 67 Qualitas projects. The 12,336 \textit{ok'} pairs
are clones between 139 Stack Overflow snippets and 43 Qualitas
projects.  Moreover, for the disagreed pairs, we found 17,081 clone
pairs reported by $S_D'$ are clones between 460 Stack Overflow
snippets and 74 Qualitas projects and 83 $N_D'$ clone pairs are clones
between 44 Stack Overflow snippets and 19 Qualitas projects. In total
we found that the filtered data sets contains 32,533 clone pairs which
are clones between 623 Stack Overflow snippets and 96 Qualitas
projects. During the manual investigation, we identified 2,420 pairs
as being accidential clones (AC), i.e.~false positives. After removing
them, the data set still contains 30,113 clone pairs between 556 Stack
Overflow snippets and 80 Qualitas projects.

\textbf{To answer RQ1, we found most Qualitas projects to share
  similar code with Stack Overflow code snippets. Depending on the
  data set, between 88 to all 111 projects share similar code. The
  filtered data set has 96 projects share code with Stack
  Overflow. Even in the manually confirmed data set of 30,113 clone
  pairs, a majority of 80 Qualitas projects share similar code with
  Stack Overflow.}

@@

Outdated code occurs when a piece of code has been copied from its
origin to another location and later the original has been
updated~\cite{Xia2014}. Usually code clone detection is used to locate
clone instances and update them to match with the
originals~\cite{Bellon2007}. However, online code clones are more
difficult to detect than in regular software projects due to its large
search space and a mix of natural and programming languages combined
in the same post.
%Moreover, Stack Overflow is not a software. There is no test suite to run and check whether the validity of the code snippets. To the best of our knowledge, this work is the first to address the problem of outdated code on Stack Overflow.

>>>>

%\subsection{Experimental Setup}
%\vspace{1ex}
To answer these four research questions, we perform an empirical study to
locate and study the online code clones between Stack Overflow and open source
projects. We designed our study in 6 phases as depicted in \Cref{fig:exp_framework} where
we build different data sets to answer each of our four research questions. 
We explain our process of building the data sets in each phase separately below.

@@

\subsection{Methodology}

\subsubsection{Phase 1: Clone Identification}

@@

\textbf{Stack Overflow:} 
We extracted Java code snippets from a snapshot of a Stack Overflow
dump\footnote{\url{https://archive.org/details/stackexchange}} in
January 2016. The archived dump has a size of 9 gigabytes. The data
dump is in XML format containing information of \textbf{Posts}
(questions and answers) and supporting data such as user accounts and
timestamps of the posts. We were interested in code snippets embedded
in posts which were located between
{\small\texttt{<code>}...\texttt{</code>}} tags. A Stack Overflow
thread contains a question and several answers. An answer can also be
marked as \textbf{accepted answer} by the questioner if the solution
fixes his/her problem. We collected Java code snippets using two
criteria. First, we only focused on code snippets in accepted
answers. We chose the snippets in accepted answers because they
actually solved the problems in the questions. Moreover, they are
always displayed just below the questions which makes them more
likely to be reused than other answers. Second, we were only
interested in code snippets of at least six lines. Snippets smaller
than six lines are usually spurious clones~\cite{Bellon2007}. Each
snippet was extracted from the dump and saved to a file.
%using its post ID as the file's name. If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g. 45051109\_0, and 45051109\_1.). Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them. 
We obtained 144,064 Java code snippets containing 2,347,267
lines\footnote{Measured by cloc:
  \url{https://github.com/AlDanial/cloc}} of Java source code.
% excluding comments and blank lines.

\textbf{Open source systems: }
We selected the established corpus for an empirical software
engineering study called \textbf{Qualitas}~\cite{QualitasCorpus} for
this study. It is a curated Java corpus that has been used in several
software engineering
studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. The
projects in the corpus represent various domains of software systems
ranging from programming languages to
visualisation~\cite{QualitasCorpus}. We selected the 20130901r release
of Qualitas corpus containing 112 Java open source projects. This
release contains projects with releases no later than 1st September
2013. We chose a snapshot late back in 2013 since we are interested in
online code clones in the direction from open source projects to Stack
Overflow. The 20130901r snapshot provides Java code that is more than
2 years older than the Stack Overflow snapshot, which is sufficiently
long for a number of code snippets to be copied onto Stack Overflow
and also to observe if clones become outdated. Out of 112 Qualitas
projects, there is one project, \textsf{jre}, that does not contain
Java source code due to its licensing limitation~\cite{QualitasCorpus}
and is removed from the study. This resulted in a total of 111
projects analysed in the study. As shown in \Cref{tab:datasets}, the
111 Qualitas project have 160,937 Java files containing 19,086,883
lines of
code. %Details of the 109 Qualitas projects and their licenses are listed in Table \ref{t:new_and_old}.

@@

\textbf{Clone Detection Tools: }
We use clone detection to discover online code clones. 
%\textbf{Clone Detection and Configuration: } 
There are a number of restrictions in terms of choosing clone
detection tools for this study. The main restriction is due to nature
of code snippets posted on Stack Overflow, as most of them are
incomplete Java classes or methods. Hence, a detector must be flexible
enough to process code snippets that are not compilable or not
complete blocks. Moreover, since the amount of code that has to be
processed is in a scale of millions line of code (as shown in
\Cref{tab:datasets}), a clone detector must be scalable enough to
report clones in a reasonable amount of time. We have tried 5
state-of-the-art clone detectors including Simian~\cite{simian},
NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002},
iClones~\cite{Gode2009}, and DECKARD~\cite{Jiang2007a} against the
Stack Overflow and Qualitas datasets. CCFinder, iClones, and DECKARD
failed with execution errors after running for couple of hours. Thus,
we removed them from the study. Simian and NiCad are flexible enough
to handle code with incomplete methods or classes and successfully
completed the detection.

@@

%We processed two datasets, 144,064 Java code snippets from accepted answers on Stack
%Overflow and 111 open source projects from the Qualitas corpus. 
%The Java code snippets were extracted from Stack Overflow posts. 
We prepared the Java code in both datasets by removing comments and
pretty-printing to increase the accuracy of clone detection. Then, we
deployed the two clone detectors to locate clones between the two
datasets. Due to a scalability issue, we partitioned the input and ran the tools multiple
times. Each run was composed of the entire Stack Overflow data and a
single Qualitas project. We repeated the process until we covered all
111 projects.  We then converted the clone reports to the General
Clone Format (GCF)~\cite{Wang2013} and combined the 111 reports into a
single GCF file.  Simian did not provide an option to detect
cross-project clones between two locations. Hence the Simian GCF clone
report was filtered to contain only clone pairs between Stack Overflow
and Qualitas projects, removing all clone pairs within either Stack
Overflow or within Qualitas. 
% NiCad provides an option to detect clones
% from two locations so no filtering was needed.

\textbf{Clone Detection Configuration: }
We were aware of effects of configurations to clone detection results
and the importance of searching for optimised configurations in
empirical clone
studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016}. However,
considering the massive size of the two datasets and the search space
of at least 15 Simian and 5 NiCad parameters, we are unable to search
for the best configurations of the tools. Thus, we decided to
configure Simian and NiCad using two established configurations:
(1)~the tools' default configurations chosen by the tools' creators
(denoted as \textit{D}), and (2)~the discovered configurations for
Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
of optimising clone detectors' configurations based on clone agreement
(denoted by \textit{E}). The details of the two configurations are
described in \Cref{t:param_tuning}.

@@

\subsubsection{Phase 2: Clone Filtering}
As there are in total 315,786,118 clone pairs reported, it is
infeasible for humans to manually validate them all. Instead of
investigating a random saple, we adopted the idea of \textbf{clone
  agreement} which has been used in clone research
studies~\cite{Funaro2010, Wang2013,cr2016ssbse} in situations where a
clone oracle is missing or impossible to establish. Clone pairs agreed
by multiple clone detection tools have a higher likelihood to be real
clones~\cite{cr2016ssbse}. By using this agreement-based approach, we
reduced the number of clone candidates for manual investigation to the
ones agreed by multiple tools. To find agreement between two clone
pairs reported by two different tools, we used the clone pair matching
metric proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs
which have a large enough number of overlapping lines can be
categorised as either a good-match or an ok-match pair (denoted as
\textit{good} and \textit{ok} respectively) with a confidence value
between 0 and 1. A \textit{good} clone pair has stronger agreement
than an \textit{ok} pair. We follow the original definitions of good-
and ok-match introduced in Bellon's paper~\cite{Bellon2007}.

@@

%\subsubsection{Filtered Clones Set}
We selected all \textit{good} pairs (2,313) and the \textit{ok} pairs for
$S_D$--$N_D$, $S_E$--$N_D$, and $S_D$--$N_E$ (12,336), but we ignored
20,021 $S_EN_E$ \textit{ok} clone pairs in the classification due to
their large number of clones and the very small average clone sizes of
5.95 and 6.28 lines (see \Cref{tab:orig_stats}), leading to a high
probability of being trivial clones. We refer to the set of clone
pairs as the \textit{good} set and the \textit{ok'} set.
Together with the 17,801 (referred as $S_D'$ set) and 83 (referred as
$N_D'$ set) clone pairs after filtering clone pairs from $S_D$ and
$N_D$, we ended up with a set of 32,533 online clone pair candidates.

Before performing the manual
investigation, we created and used an automatic classifier 
to classify boiler-plate code of {\small\texttt{equals()}}, 
{\small\texttt{hashCode()}} and getters/setters 
(depicted with a grey line in \Cref{fig:exp_framework}).
The classifier could automatically classify 28,897 clone pairs 
and left 3,636 clone pairs for manual investigation in phase 3 to 6.

\subsubsection{Phase 3-4: Clone Validation and Classification}
We relied on the 3,636 filtered clone pairs after automatic classification for
manual validation and classification.
The validation and classification of the clone pairs were done at the same time. 
The clone validation process involves checking 
if a clone pair is either true positive or false positive. 
Moreover, we are also interested in the patterns of code cloning 
so we can gain more insights into how these clones are created.

For manual investigation, the first author, who has been working on clone detection research for 
two years, took the role of the main investigator performing a manual 
validation of the filtered clone pairs. 
%By consulting the cloning patterns, 
The main investigator went through each clone pair candidate, 
looked at the clones, and decided if they are true positive or
false positive and classified them into an appropriate pattern. 
%the most appropriate cloning pattern for the pair. 
To mitigate the human errors of the manual investigation, 
the second author took the role of the validating investigator, performing a
validation on 10\% of the clone pairs judged by the main
investigator. After the validation, the results from the two
investigators were compared and conflicts were discussed and resolved.
If the two investigator cannot find a consensus, the third author is 
involved for the final judgement.

Regarding the online cloning classification patterns, 
we studied the 8 patterns of cloning from Kapser et
al.~\cite{Kapser2006,Kapser2008} and performed a preliminary study to
evaluate its applicability to our study. 
We have tried to classify 697 online clone pairs from
the reported clones in phase 1 
%Using the $S_D$ clone report,
%snippets were ranked according to (1)~clone pair frequency,
%(2)~popularity (i.e.~number of associated Qualitas projects),
%(3)~clone size in SLOC, and (4)~ratio of cloned code per snippet. We
%selected these four criteria so that we could cover the online clones
%from various aspects. We selected the top 10 from each ranking and
%obtained 34 unique Stack Overflow snippets. The snippets were
%associated with 697 clone pairs.
%\subsubsection{Defining Online Code Cloning Patterns}
using Kapser's cloning patterns. We found that the
clone pairs were categorised into either Customisation or Templating.
Thus, Kapser's cloning patterns are too broad for our study and a
more suitable and fine-grained classification scheme is needed. After
the preliminary study, we adopted one of Kapser's cloning patterns,
\emph{boiler-plate code} and \emph{API/library protocol}, and defined
6 new cloning patterns. The seven patterns include QS, SQ, EX, UD, BP,
IN, and AC as presented in \Cref{tab:classification_scheme}. Pattern
QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones
that have evidence of being copied from a Qualitas project to Stack
Overflow. The evidence of copying can be found in comments in the
Qualitas source code or in the Stack Overflow post's contents. Pattern
SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is cloning, with
evidence, in the opposite direction from Stack Overflow to a Qualitas
project. Pattern EX (\textbf{Ex}ternal Sources) is cloning that has
evidence of copying from a single or multiple external sources to
Stack Overflow and to a Qualitas project.  Pattern UD
(\textbf{U}nknown \textbf{D}irection) is cloning that creates
identical or highly similar clones between Qualitas and Stack Overflow
but where we could not find any attribution of copying.
Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones
containing boiler-plate code of {\small\verb|equals()|} methods,
getters/setters, or IDE-generated code such as GUI components. Pattern
IN (\textbf{In}heritance/Interface) is cloning by inheritance of the
same super class or implementation of the same interface. These two
activities usually result in similar overriding methods. The last
pattern, AC (\textbf{A}ccidental \textbf{C}lones), represents
accidentally similar clone pairs. These are mainly false positive
clones from the clone detectors such as similar
{\small\texttt{try-catch}} statements.

@@

\subsubsection{Phase 5: Outdated Clones}
Outdated code occurs when a piece of code has been copied from its
origin to another location and later the original has been
updated~\cite{Xia2014}. Usually code clone detection is used to locate
clone instances and update them to match with the
originals~\cite{Bellon2007}. However, online code clones are more
difficult to detect than in regular software projects due to its large
search space and a mix of natural and programming languages combined
in the same post.
%Moreover, Stack Overflow is not a software. There is no test suite to run and check whether the validity of the code snippets. To the best of our knowledge, this work is the first to address the problem of outdated code on Stack Overflow.

To search for outdated online code clones, we focused on the
\textbf{QS} clone pairs that were cloned from Qualitas to Stack
Overflow and compared them with their latest versions. We downloaded
the latest version of the Qualitas projects from their repositories on
26 September 2016. For each \textbf{QS} online clone pair, we used the
clone from Qualitas a a proxy. We searched for its latest version by
the file name and located the cloned region in the file based on the
method name.
%For Simian clones, where clones may span across several methods, we scanned upwards until we find a method name ahead of the clone region. 
We then compared the Stack Overflow snippet to its latest version
line-by-line to find if any change has been made to the source
code. We also made sure that the changes did not come from the
modifications made to the Stack Overflow snippets by the posters but
from the updates in the projects themselves. When we found
inconsistent lines between the two versions, we used
{\small\texttt{git blame}} to see who modified those lines of code and
the timestamps.

\subsubsection{Phase 6: Licensing Analysis}
Software licensing plays an important role in software
development. Violation of software licenses impacts software delivery
and also leads to legal issues~\cite{Sprigman2015}.
%It is an emerging area that software engineering research community is paying attention to. For example, 
One can run into a licensing issue if one integrates third-party
source code into their software without checking. A study by An et
al.~\cite{An2017} reports 1,219 cases of potential license violations
between 399 Android apps and Stack Overflow code
snippets.

We analysed licensing conflicts of the online clones in the
\textbf{QS}, \textbf{EX}, and \textbf{UD} set. The
licenses were extracted by \emph{Ninka}, an automatic license
identification tool~\cite{German2010}. Since Ninka works at file
level, we report the findings based on Stack Overflow snippets and
Qualitas source files instead of the clone pairs (duplicates were
ignored). For the ones that could not be automatically identified by
Ninka and have been reported as {\small\texttt{SeeFile}} or
{\small\texttt{Unknown}}, we looked at them manually to see if any
license can be found. The table shows the license mapping of Stack
Overflow snippets and Qualitas source code. The results are reported
separately for the \textbf{QS}, \textbf{EX}, and \textbf{UD} set.

%\subsection{Analysis Methods}
We followed the 6 phases in the experimental framework (\Cref{fig:exp_framework})
to answer our four research questions. 
To answer RQ1, we rely on the number of manually validated true positive online clone pairs
in phase 3. We use the results of the manual classification using the
patterns of online code cloning to answer RQ2. 
For RQ3, we looked at the true positive clone pairs that are classified 
as cloned from Qualitas to Stack Overflow and
checked if they have been changed since they have been
cloned. Similarly, for RQ4, we looked at the license of each clone in the pattern 
QS, EX, UD and checked for a possibility of a licensing violation.

@@

We followed the 6 phases in the experimental framework (\Cref{fig:exp_framework})
to answer our four research questions. 
To answer RQ1, we rely on the number of manually validated true positive online clone pairs
in phase 3. We use the results of the manual classification by the
seven patterns of online code cloning to answer RQ2 (phase 4). 
For RQ3, we looked at the true positive clone pairs that are classified 
as cloned from Qualitas to Stack Overflow and
checked if they have been changed since they have been
cloned (phase 5). Similarly, for RQ4, we looked at the license of each clone in the pattern 
QS, EX, UD and checked for a possibility of a licensing violation (phase 6).

@@

\begin{table}
\caption{Investigated online clone pairs and corresponding snippets
  and Qualitas projects for the different data sets}
\label{tab:snippets}
\centering
\begin{tabular}{l|rrrr}
  \hline 
  Data Set & Pairs & Snippets & Projects & Avg.~C$_{\textrm{\textit{\%}}}$ \\
  \hline 
  \multicolumn{5}{l}{\textit{Reported Clones}} \\
  \hline
  $S_D$ & 67,570 & 1,086 & 92 & 38\% \\
  $S_E$ & 63,635,844 & 1,531 & 111 & 50\% \\
  $N_D$ & 632,855& 1,392 & 88 & 30\% \\
  $N_E$ & 251,449,849& 12,886 & 88 & 33\% \\
  \hline
  Total & 315,786,118 & 14,856 & 111 & 38\% \\
  \hline
  \multicolumn{5}{l}{\textit{Filtered Data Set}} \\
  \hline
  \textit{good} & 2,313 & 97 & 67 & 23\% \\
  \textit{ok'} & 12,336 & 139 & 43 & 28\% \\
  $S_D'$ & 17,081 & 460 & 74 & 31\% \\
  $N_D'$ & 83 & 44 & 19 & 27\% \\
  \hline
  Total & 32,533 & 623 & 96 & 27\%\\
  \hline 
%  \multicolumn{5}{l}{\textit{Filtered Data Set without AC}} \\
%  \hline 
%  $\textit{good}/\textrm{AC}$ & 141 & 52 & 26 & 23\% \\
%  $\textit{ok'}/\textrm{AC}$ & 12,229 & 126 & 36 & 28\% \\
%  $S_D'/\textrm{AC}$ & 17,673 & 448 & 72 & 31\% \\
%  $N_D'/\textrm{AC}$ & 70 & 39 & 16 & 29\% \\
%  \hline
%  Total & 30,113 & 556 & 80 & 28\% \\
%  \hline
  \multicolumn{5}{l}{\textit{True Positives in Manually Validated Clones}} \\
  \hline 
  $\textit{good}/\textrm{AC}$ & 131 & 51 & 24 & 22\% \\
  $\textit{ok'}/\textrm{AC}$ & 152 & 83 & 22 & 21\% \\
  $S_D'/\textrm{AC}$ & 873 & 337 & 60 & 35\% \\
  $N_D'/\textrm{AC}$ & 60 & 33 & 15 & 27\% \\
  \hline
  Total & 1,216 & 516 & 75 & 26\% \\
  \hline
\end{tabular}
\end{table}

However, using Bellon's criteria for matching clone pairs, only
0.1\textperthousand~of all pairs are agreed by two tool/configuration
combinations. As shown in \Cref{tab:snippets}, for the 2,313
\textit{good} pairs, there are 97 Stack Overflow snippets which are
associated with 67 Qualitas projects. The 12,336 \textit{ok'} pairs
are clones between 139 Stack Overflow snippets and 43 Qualitas
projects.  Moreover, for the disagreed pairs, we found 17,081 clone
pairs reported by $S_D'$ are clones between 460 Stack Overflow
snippets and 74 Qualitas projects and 83 $N_D'$ clone pairs are clones
between 44 Stack Overflow snippets and 19 Qualitas projects. In total
we found that the filtered data sets contains 32,533 clone pairs which
are clones between 623 Stack Overflow snippets and 96 Qualitas
projects.

During the manual investigation of 3,636 clone pairs, we identified 2,420 pairs
as being accidential clones (AC), i.e.~false positives. After removing
them, the data set still contains 1,216 true positive clone pairs between 516 Stack
Overflow snippets and 75 Qualitas projects.

\textbf{To answer RQ1, we found most Qualitas projects to share
  similar code with Stack Overflow code snippets. In the manually confirmed 
  data set of 3,636 clone pairs, we found 1,216 pairs as true positives and 
  they account for a majority of 75 Qualitas projects and
  516 Stack Overflow code snippets.}

@@
